---
title: "Untitled"
author: "Aditya Venkataraman"
date: "4/9/2017"
output: html_document
---

```{r}
employment <- read.csv("Employment.csv")
monthly <- read.csv("MonthlySample.csv")
unemployment <- read.csv("Unemployment.csv")
party <- read.csv("PartyControl.csv")


m1 <- merge(employment, unemployment, by.x = "Star.Year", by.y = "Star.Year")
merged_f <- merge(m1,party,by.x = "Star.Year", by.y = "Star.Year")
merged_f$Annual.Average.x <- NULL
merged_f$Annual.Average.y <- NULL
write.csv(merged_f,"party_all.csv")

```



First pass at looking at the different parties against the unemployment/employment Ratio. 

```{r}
library(ggplot2)
library(gridExtra)

party$Senate <- as.factor(party$Senate)

#Biased Romulan Unemployment
romulan_prez_data <- subset(party, President == "R")


#Romulan President Unemployment
romulan_results2 <- ggplot(data = romulan_prez_data,aes(x=Star.Year, y=Unemp.Emp.Ratio))+geom_line()
romulan_results2

#Romulan Senate
romulan_senate_data <- subset(party, Senate == "R " | Senate == "R")
romulan_results3 <- ggplot(data = romulan_senate_data,aes(x=Star.Year, y=Unemp.Emp.Ratio))+geom_line()
romulan_results3

#Romulan HoR
romulan_house_data <- subset(party, House == "R " | House == "R")
romulan_results4 <- ggplot(data = romulan_house_data,aes(x=Star.Year, y=Unemp.Emp.Ratio))+geom_line()
romulan_results4




klingon_prez_data <- subset(party, President == "K")
klingon_results1 <- ggplot(data = klingon_prez_data,aes(x=Star.Year, y=Unemp.Emp.Ratio))+geom_line()
klingon_results1

klingon_senate_data <- subset(party, Senate == "K ")
klingon_results2 <- ggplot(data = klingon_senate_data,aes(x=Star.Year, y=Unemp.Emp.Ratio))+geom_line()
klingon_results2

klingon_house_data <- subset(party, House == "K " & Star.Year < 2342)
klingon_results3 <- ggplot(data = klingon_house_data,aes(x=Star.Year, y=Unemp.Emp.Ratio))+geom_line()
klingon_results3






```


Next Step would be to start looking into Combinations of these and looking into a more granular picture to get a mre accurate/distorted picture....

```{r}


plot1 <- ggplot(data = klingon_prez_data, aes(Star.Year)) + 
      geom_point(aes(y = Unemp.Emp.Ratio, colour = "red"))

plot1+geom_point(data = romulan_prez_data, aes(y = Unemp.Emp.Ratio, colour = "blue"))


plot2 <- ggplot(data = merged_f, aes(Star.Year)) + 
    geom_point(aes(y = Unemp.Emp.Ratio, color = President))
plot2<-plot2+geom_line(aes(y = Unemp.Emp.Ratio),linetype="dotted")

plot3 <- ggplot(data = merged_f, aes(Star.Year)) + 
    geom_point(aes(y = Unemp.Emp.Ratio, color = Senate))
plot3<-plot3+geom_line(aes(y = Unemp.Emp.Ratio),linetype="dotted")

plot4 <- ggplot(data = merged_f, aes(Star.Year)) + 
    geom_point(aes(y = Unemp.Emp.Ratio, color = House))
plot4<-plot4+geom_line(aes(y = Unemp.Emp.Ratio),linetype="dotted")

grid.arrange(plot2,plot3,plot4, ncol=1)



diffvec <- diff(merged_f$Unemp.Emp.Ratio)
diffvec <- c(0,diffvec)

merged_f$diffv <- diffvec
num_House <- as.numeric(substr(merged_f$House.Majority.., 1, 2))
for(i in 1:65) 
{
  if(merged_f$House[i] == "R" | merged_f$House[i] == "R ")
  {
    
    num_House[i] <- num_House[i] - 50
  }
  else{
    num_House[i] <- 50 - num_House[i] 
    
  }

}

merged_f$house_skew <- num_House



p<-ggplot(merged_f, aes(x=house_skew, y=diffv)) +
  geom_point() +
  lims(x=c(-20,20), y = c(-0.03,0.05)) +
  theme_minimal() +  
  geom_vline(xintercept = 0) + geom_hline(yintercept = 0) 
p




num_Senate <- as.numeric(substr(merged_f$Senate.Majority.., 1, 2))
for(i in 1:65) 
{
  if(merged_f$Senate[i] == "R" | merged_f$Senate[i] == "R ")
  {
    
    num_Senate[i] <- num_Senate[i] - 50
  }
  else{
    num_Senate[i] <- 50 - num_Senate[i] 
    
  }

}

merged_f$senate_skew <- num_Senate

p2<-ggplot(merged_f, aes(x=senate_skew, y=diffv)) +
  geom_point() +
  lims(x=c(-10,18), y = c(-0.03,0.05)) +
  theme_minimal() +  
  geom_vline(xintercept = 0) + geom_hline(yintercept = 0) 
p2

```


Percent Change in Unemployement Rate, say senate or house changed one year, did the unemp.emp.ratio increase?
  -Tryna compare percentage (either house or senate control) to percent change in unemp.emp.ratio.
  -We care more about "by that year in power, what is the percent"
